\section{Conclusion}
This project successfully developed a robust predictive model for house prices using a hybrid Autoencoder-LSTM architecture. The model effectively addressed the challenges posed by the high dimensionality and sequential nature of the dataset. Key accomplishments include:

\begin{itemize}
    \item \textbf{High Predictive Accuracy:} The model achieved an R² score of 0.994, demonstrating its ability to explain nearly all variance in house prices.
    \item \textbf{Efficient Dimensionality Reduction:} The autoencoder compressed high-dimensional data into a latent space while retaining essential patterns, reducing noise and improving computational efficiency.
    \item \textbf{Temporal Dependency Modeling:} The LSTM layers captured long-term dependencies in the data, enabling accurate time-series predictions.
    \item \textbf{Generalization:} The model exhibited consistent performance across training, validation, and testing datasets, showcasing its robustness and adaptability.
\end{itemize}

These results highlight the effectiveness of combining autoencoders and LSTMs for predictive modeling in complex datasets such as those involving real estate markets. The insights provided by this model can assist stakeholders, including buyers, sellers, and policymakers, in making informed decisions.

\section{Future Work}
While the model demonstrates strong performance, there are opportunities for further enhancements:

\begin{itemize}
    \item \textbf{Scalability Across Regions:} Extend the model to predict house prices for multiple cities or regions, testing its adaptability to different market conditions and demographic trends.
    \item \textbf{Inclusion of Additional Features:} Incorporate external factors such as employment rates, population growth, or geographic attributes to improve the model's comprehensiveness and accuracy.
    \item \textbf{Advanced Hyperparameter Tuning:} Conduct extensive hyperparameter optimization using techniques like grid search or Bayesian optimization to further refine model parameters.
    \item \textbf{Incorporating Seasonal Trends:} Integrate seasonal and cyclical patterns explicitly into the model to capture housing market dynamics better.
    \item \textbf{Real-Time Deployment:} Deploy the model as a real-time prediction tool, allowing stakeholders to access up-to-date house price forecasts through an interactive application or API.
    \item \textbf{Alternative Architectures:} Explore advanced architectures such as Transformer-based models to improve sequential modeling and capture complex relationships more effectively.
    \item \textbf{Explainability:} Enhance model explainability by integrating techniques such as SHAP or LIME to provide insights into feature importance and model decisions.
\end{itemize}

By addressing these areas, the model can be expanded to serve broader applications in real estate analytics and decision-making, enabling more informed and data-driven strategies for various stakeholders.
